\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage{enumitem}
  \setlist[itemize]{nosep, topsep=3pt, left=1em, label=\textbullet}
\usepackage[hidelinks]{hyperref}
  \hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\usepackage{titlesec}
  \titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
  \titlespacing*{\section}{0pt}{1.5ex plus .5ex minus .2ex}{1ex plus .2ex}
\usepackage{needspace}
\usepackage{fontawesome5}

\setlength{\parindent}{0pt}

\begin{document}

% --- Header ---
\begin{center}
  {\LARGE\bfseries Adnan Ahmed Khan}\\[0.4em]
  \href{mailto:khanadnanahmed01@gmail.com}{khanadnanahmed01@gmail.com} \quad|\quad
  \href{https://linkedin.com/in/adnahmed}{linkedin.com/in/adnahmed} \quad|\quad
  \href{https://github.com/adnahmed}{github.com/adnahmed}
\end{center}

% --- Profile ---
\section*{Profile}
Full-Stack \& Mobile Lead with 5 years of experience specializing in distributed systems, high-performance backend engineering, and cloud-native architectures. Proven record of transforming monolithic systems for horizontal scalability and reducing critical API latency by up to \textbf{96\%}. Expert in leading cross-functional teams and modernizing CI/CD pipelines for production-grade cloud infrastructures.

% --- Work Experience ---
\section{Work Experience}

% Job 1: HackOnTech
\noindent \textbf{\href{https://hackontech.com/}{HackOnTech}} \hfill Islamabad, Pakistan

\textit{Team Lead} \hfill Sep 2024 -- Present
\begin{itemize}
     \item Lead a cross-functional team of \textbf{7 developers}, driving architectural decisions and the delivery of high-availability cloud services on \textbf{AWS}.
    \item Modernized CI/CD pipelines using \textbf{Terraform} and \textbf{GitHub Actions} to support daily deployments and automated infrastructure provisioning. 
    \item Reduced production hotfix frequency by establishing automated testing, static analysis, and strict code review standards.
    \item Mentor junior engineers in clean architecture and distributed system thinking, improving team output consistency.
\end{itemize}

\needspace{4\baselineskip}
\textit{Full Stack Developer} \hfill Apr 2023 -- Sep 2024
\begin{itemize}
    \item Built a dynamic \textbf{Node.js query builder} that reduced critical API latency from 30s+ to \textbf{<1s} by optimizing complex PostgreSQL operations.
    \item Re-architected a monolithic backend into \textbf{horizontally scalable microservices} using \textbf{Docker} and \textbf{AWS EKS}, handling millions of records.
    \item Implemented hardened API security with \textbf{JWT}, layered validation, and \textbf{AWS WAF} to protect sensitive data.
\end{itemize}
{\small \textbf{Tech:} TypeScript, Node.js, Nest.js, AWS (EKS, Lambda, S3), Terraform, Postgres, Redis, Docker, CI/CD.}

\vspace{1.2em}

% Job 2: Creative IT Park (NEW)
\noindent \textbf{\href{https://creativeitpark.org/}{Creative IT Park}} \hfill Islamabad, Pakistan

\textit{Software Engineer} \hfill Feb 2021 -- Mar 2023
\begin{itemize}
    \item Scaled 10+ diverse products (SaaS, Portals, E-commerce) by implementing a robust backend architecture using \textbf{Node.js}, \textbf{Python}, and \textbf{AWS (ECS, RDS)}.
    \item Improved search performance and data retrieval speed by \textbf{70\%} through the integration of \textbf{ElasticSearch} and \textbf{ElastiCache (Redis)}.
    \item Architected high-concurrency event-driven systems using \textbf{Kafka} and \textbf{Serverless} functions to handle real-time data processing for AI-driven applications.
    \item Developed secure healthcare and fintech integrations using \textbf{FHIR} standards and \textbf{OAuth 2.0}, ensuring industry-grade compliance.
    \item Established a component-driven frontend workflow with \textbf{React}, \textbf{Redux Toolkit}, and \textbf{Storybook}, reducing UI development time by \textbf{40\%}.
\end{itemize}
{\small \textbf{Tech:} React.js, TypeScript, Node.js, Python, AWS (ECS, Kafka), Docker, Kubernetes, PostgreSQL, MongoDB, FHIR, Jest.}

\vspace{1.2em}

% Job 3: GeekGenix
\needspace{4\baselineskip}
\noindent \textbf{\href{https://www.geekgenix.com/}{GeekGenix}} \hfill Islamabad, Pakistan\\
\textit{Backend Developer} \hfill Dec 2020 -- Feb 2021
\begin{itemize}
    \item Integrated \textbf{Stripe} for secure payments and connected endpoints seamlessly with a React frontend.
    \item Implemented authentication using \textbf{Passport.js} and strengthened reliability through Jest-based unit testing.
    \item Designed RESTful APIs with Express.js \& MongoDB to support dynamic customer workflows.
\end{itemize}

{\small \textbf{Tech:} Node.js, Express.js, MongoDB, React, Passport.js, Stripe API, Jest.}

% --- Education ---
\section{Education}

\textbf{BS Computer Science} \hfill Sep 2018 -- Feb 2023\\
\href{https://www.uaar.edu.pk/}{PMAS Arid Agriculture University}, Rawalpindi

\vspace{0.5em}
\textbf{FSc Pre-Engineering} \hfill Mar 2016 -- Mar 2018\\
\href{https://icb.edu.pk/}{Islamabad College for Boys}, Islamabad

% --- Projects ---

\needspace{6\baselineskip}
\section{Projects}

% PROJECT 1: Vidx
\textbf{\href{https://clipifie.com/}{Vidx}} \hfill
\href{https://github.com/adnahmed/vidx-infra}{\faGithub} \quad | \quad May 2025 -- Oct 2025
\begin{itemize}
    \item Architected a distributed video-rendering platform using \textbf{FastAPI} and \textbf{React}, supporting 50+ cinematic transitions.
    \item Built a non-blocking parallel pipeline using \textbf{RabbitMQ + Celery}, dynamically scaling workers based on CPU/GPU availability.
    \item Compiled a custom \textbf{FFmpeg} build with GL-Transitions to enable \textbf{4K rendering} while reducing memory overhead.
\end{itemize}
{\small \textbf{Tech:} FastAPI, React, RabbitMQ, Celery, Docker, MongoDB, Traefik, FFmpeg.}

\vspace{1em}

% PROJECT 2: Crackq
\needspace{5\baselineskip}
\textbf{\href{https://hashcrack-git-dev-adnan-repo.vercel.app/}{Crackq.me}} \hfill
\href{https://github.com/adnahmed/hashcrack}{\faGithub} \quad | \quad Feb 2023 -- Dec 2023
\begin{itemize}
    \item Built a SaaS platform for distributed cryptographic hash cracking using \textbf{Next.js} and containerized workers.
    \item Leveraged \textbf{Fitcrack (BOINC)} to orchestrate a global grid of GPU nodes, enabling on-demand scaling without downtime.
\end{itemize}
{\small \textbf{Tech:} Next.js, TypeScript, Docker, Hashcat, Fitcrack/BOINC.}

\vspace{1em}

% PROJECT 3: pdf-annotate.js
\needspace{5\baselineskip}
\textbf{\href{https://github.com/adnahmed/pdf-annotate.js}{pdf-annotate.js}} \hfill
\href{https://github.com/adnahmed/pdf-annotate.js}{\faGithub} \quad | \quad Mar 2024 -- Apr 2024
\begin{itemize}
    \item Added a remote StoreAdapter enabling \textbf{real-time annotation sync} with a central API.
    \item Optimized SVG/TypeScript rendering logic to prevent annotation overlap and improve interactive performance.
\end{itemize}
{\small \textbf{Tech:} PDF.js, TypeScript, SVG.}

\end{document}
